### 2016-04-21 writing/latex/coincidence.tex
Add references, add appendages

We know that there are a total of \(512\) mesh-sets for each underlying classical
pattern. By use of the shading lemma, simultaneous shading lemma, and
one special case, we can reduce the number of equivalence classes to \(220\).

@@

\end{tikzpicture}
    \caption{An illustration of how lines and points move by this proposition.}
\end{figure}

@@

>>>>

We know that there are a total of \(512\) mesh-sets for each underlying classical
pattern. By use of the previous results of the Shading
Lemma\cite[Lemma~3.11]{DBLP:journals/combinatorics/HilmarssonJSVU15},
Simultaneous Shading Lemma\cite[Lemma~7.6]{DBLP:journals/corr/ClaessonTU14}, and
one special case, we can reduce the number of equivalence classes to \(220\).

@@

\end{tikzpicture}
    \caption{If the conditions of \PropositionRef{prop:dom2} are satisfied the box
    \((a-1,b)\) can be shaded.}
\end{figure}

@@

By application of this rule we can reduce the number of classes in
\(\av{\{\perm{2,3,1},(\perm{1,2}, R)\}}\) to \(56\).

### 2016-04-21 writing/latex/introduction.tex
Add references, add appendages

\chapter{Introduction\label{cha:introduction}}
\section{What is a Permutation?}
In \emph{The Art of Computer Programming} Donald Knuth defines
A \emph{permutation of \(n\) objects} is an arrangement of \(n\) distinct
objects in a row. When considering permutations we can consider them as
occuring on the set \(\nrange{n} = \setrange{1}{n}\), therefore a permutation
is a \emph{bijection} \(\pi:\nrange{n} \mapsto \nrange{n}\). We can write a
permutation \(\pi\) in two line notation
\begin{equation*}
\pi = \twoline{1,2,\dotso,n}{\pi(1),\pi(2),\dotso,\pi(n)}
\end{equation*}
However, the most frequent notation used in computer science is
\emph{one-line notation}, in this form we drop the top line of the two line
notation so are left with the following.
\begin{equation*}
\pi = \perm{\pi(1),\pi(2),\dotso,\pi(n)}
\end{equation*}

@@

We can display a permutation on a \emph{figure} in order to give a graphical
representation of the permutation. In such a figure we let the \(x\)-axis
denote the index in the permutation, and the \(y\)-axis denotes the values of
\(\pi(x)\). The figure of the permutation \(\pi = \perm{2,3,1}\) is shown below
\begin{equation*}
    \pattern{}{2,3,1}{}
\end{equation*}

@@

\section{Classical Permutation Patterns}
Classical Permutation Patterns began to be studied as a result of Knuth's
statements about stack-sorting in [The Art of Computer Programming].

@@

\section{Mesh Patterns}
Mesh Patterns were introduced by Brändén and Claesson to capture explicit expansions
for certain permutation statistics. They are a natural extension of Classical
permutation patterns. A \emph{mesh-pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq
    [0,k]\times [0,k].
\end{equation*}
By this definition the empty permutation \(\varepsilon\) as a mesh pattern consisting solely of the
box \((0,0)\).

>>>>

\chapter{Introduction\label{cha:introduction}}
\section{What is a Permutation?}
In \emph{The Art of Computer Programming}\cite[p.~45]{Knuth:1997:ACP:260999} Donald Knuth defines
A \emph{permutation of \(n\) objects} is an arrangement of \(n\) distinct
objects in a row. When considering permutations we can consider them as
occuring on the set \(\nrange{n} = \setrange{1}{n}\), therefore a permutation
is a \emph{bijection} \(\pi:\nrange{n} \mapsto \nrange{n}\). We can write a
permutation \(\pi\) in two line notation
\begin{equation*}
\pi = \twoline{1,2,\dotso,n}{\pi(1),\pi(2),\dotso,\pi(n)}
\end{equation*}
However, the most frequent notation used in computer science is
\emph{one-line notation}, in this form we drop the top line of the two line
notation so are left with the following.
\begin{equation*}
\pi = \perm{\pi(1),\pi(2),\dotso,\pi(n)}
\end{equation*}

@@

We can display a permutation on a \emph{figure} in order to give a graphical
representation of the permutation. In such a figure we let the \(x\)-axis
denote the index in the permutation, and the \(y\)-axis denotes the values of
\(\pi(x)\). The figure of the permutation \(\pi = \perm{2,3,1}\) is shown below
\begin{equation*}
    \pattern{}{2,3,1}{}
\end{equation*}
It is convenient to call the elements of the permutation \emph{points} when
referring to these figures.

@@

\section{Classical Permutation Patterns}
Classical Permutation Patterns began to be studied as a result of Knuth's
statements about stack-sorting in \emph{The Art of Computer Programming}
\cite[p.~243, Ex.~5,6]{Knuth:1997:ACP:260999}.

@@

\section{Mesh Patterns}
Mesh Patterns were introduced by Brändén and Claesson\cite{journals/combinatorics/BrandenC11} to capture explicit expansions
for certain permutation statistics. They are a natural extension of Classical
permutation patterns. A \emph{mesh-pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq
    [0,k]\times [0,k].
\end{equation*}
By this definition the empty permutation \(\varepsilon\) as a mesh pattern consisting solely of the
box \((0,0)\).
